---
title: "Chapter report for stock XX"
date: "May `r format(Sys.Date(), '%Y')` (updated: `r Sys.Date()`)"
lang: en
format: docx
editor: source
number-sections: true
crossref:
  chapters: true
---


```{r, general_variable,  include = FALSE}
library("here")
library("icesTAF")
library("icesAdvice")
library("FLCore")
library("tidyverse")
library("flextable")

assessment_year <-  as.numeric(format(Sys.time(), "%Y"))
data_year <- assessment_year - 1

#knitr option
knitr::opts_chunk$set(
  include = TRUE,        
  echo = FALSE,
  cache = FALSE,
  warning = FALSE,
  message = FALSE,
  progress = FALSE,
  verbose = FALSE,
  # dev = 'png',
  fig.height = 8,
  fig.width = 8,
  dpi = 300,
  # out.width = 700,
  # out.height = 550,
  # fig.retina = 1,
  autodep = FALSE,
  knitr.duplicate.label = 'allow')

options(scipen = 999)

in_tonnes <- function(x){
  prettyNum(x, big.mark = " ")
}

round_tonnes <- function(x){
  round(x, digits = -2)
}
caption_prefix <- "Bay of Biscay sole (S. solea) in divisions 8.a and 8.b."
```

```{r, load-data-output,  include = FALSE}
# here load data, model fit and outputs to make figures and tables
``` 

#	Stock XX

## General

### Type of assessment in `r assessment_year`

### Ecosystem aspects

### Fisheries

### Summary of ICES advice for  `r assessment_year -2` and Management regulations

#### ICES advice for  `r assessment_year - 1` (as extracted from ICES Advice `r assessment_year -2`)

#### Management applicable for `r assessment_year - 1` and `r assessment_year`

#### Additional information provided by the fishing industry

## Data

### Catches

#### ICES catch estimates (InterCatch)

#### Reconstruction of discards

#### Numbers-at-age

Catch, landings and discards numbers-at-age are shown in @fig-n-at-age-year, @fig-catch-age, @fig-landings-age, fig-discards-age and @tbl-catch-age.

#### Weight-at-age

Weights-at-age for discards and landings are shown in @fig-discards-wt and @fig-landings-wt respectively and
weights-at-age in the catch are given in Figure @fig-catch-wt and @tbl-catch-wt.

### Stock weight-at-age

Stock weights-at-age are shown in @fig-stocks-wt and @tbl-stock-wt. 

### Maturity and natural mortality

#### Maturity

(see Stock Annex, @tbl-maturity).

#### Natural mortality

The final values of natural mortality used in the stock assessment model are listed in @tbl-M.

## Tuning series

### French BTS-VIII surveys index

Figures @fig-bts-viii and @tbl-index-bts-viii provide the index used as input in the stock assessment model.
 @fig-bts-viii-internal-cst provides cohort consistencies, which shows that the index tracks well the cohorts.


### French commercial otter trawl LPUE index

@tbl-lpue-trawler and @fig-lpue-trawler provide the index used as input in the stock assessment model. 

## Assessment

### Input data

Details on the preparation of input data for the stock assessment are provided in stock annex. 
@fig-SAM-dataplot shows the different time series used in the model.

### Model

R codes used to produced run the model, extract results and perform forecasts are available within the Transparent Assessment Framework (TAF, https://github.com/ices-taf/2024_sol.27.8ab_assessment.git).
The full description of the SAM configuration file is provided in @tbl-sam-conf-file.

### Assessment results

The SAM model fitting diagnostics and survey catchabilities are shown in @tbl-sam-diag-fit and @tbl-catchability-index respectively.
The assessment summary is given in @tbl-summary-conf and @fig-SAM-summary.

The F-at-age shows that the selectivity of the fishery changed over time  (@tbl-Fatage and @fig-SAM-f-at-age).

The process residuals do not indicate any major problems with respect to the model configuration @fig-SAM-resids-process and @fig-SAM-resids-process-summary.

The one step ahead residuals for the catch, BTS-VIII and French Trawler LPUE data do not indicate strong patterns across ages and years  @fig-SAM-resids-obs and @fig-SAM-resids-obs-summary.

The retrospective pattern shows a good estimation of F, SSB for `r assessment_year - 3` data @fig-SAM-retro.
The @tbl-MohnRho gives the results of the Mohn’s rho calculation that is the results from the most recent assessments and five retrospective assessments with terminal years (`r assessment_year - 5`–`r assessment_year - 1 `).
Mohn’s Rho value is `r  filter(tab_mohn_roh, Variable == "R(age 2)") %>% pull(Value)` for the recruits, `r filter(tab_mohn_roh, Variable == "SSB") %>% pull(Value)` for SSB and `r filter(tab_mohn_roh, Variable == "Fbar(3-7)") %>% pull(Value)` for F.

### Historical stock trends

Trends in catch, SSB, Fbar and recruitment are presented in @tbl-summary-conf and @fig-SAM-summary.

### Short term forecast

The STF parameters for intermediate years are available in @tbl-stf-parameter and the results of the STF using different scenarios are presented in @tbl-management.

### Biological reference points

### Quality of the assessment

#### Comparison with last advice

Short-term forecast assumptions comparison for `r assessment_year` and `r data_year` are provided in @fig-stf-assumption-comparison.
For each variable used in forecasts (Fbar, Recruitment, SSB and Total catch) changes are observed between `r assessment_year` and `r data_year`.

@fig-plot-n-at-age-comparison and @fig-plot-w-at-age-comparison show the ratio of the number-at-age and weights-at-age estimated in `r assessment_year` and `r data_year`.
@fig-plot-B-at-age-comparison shows the biomass at age between the two assessments.

### Benchmark issue list

#### Data issues

#### Assessment issues

#### Short-term forecast issues

### Management considerations

## References


### Tables and figures

```{r child = here("R", "report", "report_tables.qmd"), eval = TRUE}
```

```{r child = here("R", "report", "report_figures.qmd"), eval = TRUE}
```
